### 2019-06-25 TFM.tex
Casi fin

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{fact}{Fact}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{propdef}{Proposition / Definition}[chapter]
\theoremstyle{remark}
\newtheorem{remark}{Remark}[chapter]

\newtheorem{inneraxiom}{Axiom}
\newenvironment{axiom}[1]
{\renewcommand\theinneraxiom{#1}\inneraxiom}
{\endinneraxiom}

\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{c_{i_1}, \cdots, c_{i_m}}
\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}

\begin{document}
\tableofcontents

@@

\chapter*{Notation}

@@

After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
$G$ a random graph in $G(n,\beta/n)$. We define the events $E_1,\dots,E_{n_k}$ as
\[E_i:= (G \models \phi) \wedge (G \in C_i),\]
and the  event $F$ as
\[F:= (G \models \phi) \bigwedge_{i=1}^{n_k} (G \notin C_i).\]
Then, for any $n\in \N$
\begin{equation} \label{eqn:sumevents}
P(G\models \phi) = \sum_{i=1}^{n_k} P(E_i)  + P(F),
\end{equation}
as the events $E_i$ together with $F$ form a partition of all the cases where $G$ satisfies $\phi$. \par

Fix and index $i\in \{1, \dots, n_k\}$. From the property (1) of the classes $C_1,\dots, C_{n_k}$ 
it follows that if $G$ and $H$ are random graphs, then
\[\Ln P((G\models \phi) \wedge \neg(H\models \phi) \, | \, G\in C_i \wedge H\in C_i \, ) = 0.\]
This is because $G$ and $H$ share a.a.s the same rank $k$ type if they both belong to $C_i$. 
In consequence the limit
\[ \Ln P(G\models \phi \, | \, G\in C_i )\] 
is either zero or one, and 
\begin{equation}\label{eqn:property1}
\Ln P(E_i)= \Ln P(G\in C_i)\cdot P(G\models \phi \, | \, G\in C_i)= \text{ either } 0 \text{ or } \Ln P(G\in C_i).
\end{equation} 
\par 
Also, as a consequence of property $(2)$ we obtain
\[\Ln P(\bigwedge_{i=1}^{n_k} G \notin C_i)=0, \] 
so
\begin{equation}\label{eqn:property2}
\Ln P(F)= \Ln P(\bigwedge_{i=1}^{n_k} G \notin C_i)\cdot P(G\models \phi \, | \, \bigwedge_{i=1}^{n_k} G \notin C_i)=0.  
\end{equation}
\par
Taking limits in equation \ref{eqn:sumevents} and using equations \ref{eqn:property1} and \ref{eqn:property2} 
we get
\[ \Ln P(G\models \phi) = \sum\limits_{C_i\in \mathcal{C}} \Ln P(G \in C_i) ,\]
where $\mathcal{C}$ is a (possibly empty) subset of $\{C_1,\dots, C_{n_k}\}$.
Finally, because of property (3) for each $i$ the limit $\Ln P(G \in C_i)$ is 
an expression in $\Theta$. Thus $\Ln P(G\models \phi)$ is a finite sum of expressions in $\Theta$
and the theorem follows. \par

@@

\section{Agreability Classes}

@@

\chapter{First Order Logic of Sparse Random General Hypergraphs}

\section{General Hypergraphs}

$\forall n\in N: \quad [n]:= \{1,\dots, n\}$\par
$S_n:$ symmetric group on $n$ elements. \par
Let $X$ be a set, then:
\begin{itemize}
	\item $\Delta\subset X^2:$ $\Delta$ is the diagonal subset. $\Delta: \{(a,a)\in X^2 \}$.
	\item $S_n$ acts on $X^n$ in the obvious way. 
	\item When the subgroup $\phi$ is understood or (is not relevant) $\langle x_1,\dots,x_n\rangle$
	denotes the equivalence class of $(\vlst{x}{n})$ in $X^n/\phi$.
\end{itemize}
\par

\begin{definition}
	Let $V$ be a finite set. Given a natural number $a\in \N$, a group $\phi\leq S_a$ and a subset
	$R\subseteq [a]^2 \setminus \delta$, the total (hiper-)edge set of size $a$, symmetry group $\phi$ and
	restrictions $R$ is the set:
	\[ \mathcal{H}_{V,a}^{\phi,R}= V^n/\phi \, \, \setminus \{\,  \langle 
	x_1, \dots,x_n\rangle
	 \in V^n/\phi  \, \, | \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]

\end{definition}

\begin{definition}
	An hypergraph $(V,H_1,\dots, H_l)$ with edge sizes $a_1,\dots,a_l$, 
	symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$ consists of
	\begin{itemize}
		\item A finite vertex set $V$.
		\item For $i=1,\dots,l$, an edge set $H_i\subseteq \mathcal{H}_{V,a_i}^{\phi_i,R_i}$.
	\end{itemize}
\end{definition}

\begin{definition} 
	Random model $G(n, p_1,\dots, p_l)$ with edge sizes $a_1,\dots,a_l$, 
	symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$:
	\begin{itemize}
		\item We obtain a hypergraph $(V,H_1,\dots, H_l)$ with $V=[n]$
		\item The probability of each edge $e\in \mathcal{H}_{V,a_i}^{\phi_i,R_i}$
		is $p_i$ independently. 
	\end{itemize}
\end{definition}

From now on we fix the edge sizes $a_1,\dots,a_l$, 
symmetry groups $\phi_1,dots,\phi_1$ and restrictions $R_1,\dots,R_l$. \par

In a graph $G(V,E_1,\dots, E_l)$, the type of an edge $e$ is the index
$i$ such that $e\in E_i$.

The language is the first order relational 
language with relations $R_1,..., R_l$ of arities
$a_1,\dots, a_l$ respectively. The interpretation on 
$(V,H_1,\dots, H_l)$ is the evident one. \par

\begin{definition}
	The characteristic $ch(G)$ of an hypergraph $G=(V,E_1,\dots,E_l)$ is
	\[ \left( \sum_{i=1}^l |E_i|(a_i-1)\right) -	|V|  .\]
	An hypergraph is c-balanced if it contains no subgraph of
	greater characteristic than itself. 
\end{definition}

\begin{proposition}
	A connected graph cannot have characteristic lesser than $-1$.
\end{proposition}

\begin{definition}
	A unicycle is a connected c-balanced graph with characteristic $0$.
\end{definition}

\begin{definition} A cluster is a minimal c-balanced graph.
\end{definition}

Remark: Note that clusters have to be connected.

\begin{definition}
	A cycle is a minimal unicycle, or equivalently a characteristic $0$ cluster.  
\end{definition}

\begin{proposition}
	Any unicycle contains exactly one cycle. 
\end{proposition}

\begin{definition} 
	A (hiper)forest is a graph with no clusters. A (hiper)tree is a connected forest.
\end{definition}

@@

\begin{proposition} There is a unique path between any two vertices of a tree. 
\end{proposition}

We define the constant set $Const:=\{c_i\}_{i\in \N}$.

\begin{definition} 
	As before, a (hiper)graph with constants $G(\clist)$ is a hypergraph 
	$G$ together with a co-labeling. 
\end{definition}

@@

We define a distance over $G(\clist)$.
\[ d(x,y)= (\text{minimum size of a connected graph containing }x \text{ and } y) - 1 \]
If such graph does not exist we define $d(x,y)=\infty$.\par

Given $x\in V(G)$ and $X\subseteq V(G)$ we define $N(x;r)$ and $N(X;r)$ as
\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | dist(x,y)\leq r \, \} \]
\[ N(X;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | dist(X,y)\leq r \, \}. \]

\begin{definition}
	 A rooted (hiper)tree is a tree with a distinguished vertex called root.
	 The radius of the tree is the maximum distance between its root and any
	 of its vertices.  
\end{definition}

In a rooted tree $(T,x)$ all the (hiper)edges can be rooted in a canonical way. 
The root of an edge $e$ is the vertex $y\in e$ such that $dist(x,y)=dist(x,e)$.

\begin{definition}
	Let $G(\clist)$ be a graph with constants and $x\in V(G)$. Then
	$Tree(x,G)=(G[V_x],x)$, where
	\[ V_x= \{\, y\in V \, | \, dist(Center(G),y)= dist(Center(G),x)+ dist(x,y) \,	 \}. \]
\end{definition}

>>>>

\newtheorem{proposition}{Proposition}[chapter]
\newtheorem{fact}{Fact}[chapter]
\newtheorem{theorem}{Theorem}[chapter]
\newtheorem{lemma}{Lemma}[chapter]
\newtheorem{corollary}{Corollary}[chapter]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[chapter]
\newtheorem{propdef}{Proposition / Definition}[chapter]
\newtheorem{remark}{Remark}[chapter]

\newtheorem{inneraxiom}{Axiom}
\newenvironment{axiom}[1]
{\renewcommand\theinneraxiom{#1}\inneraxiom}
{\endinneraxiom}
\newcommand{\cc}{\mathfrak{c}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Hc}{\mathcal{H}}
\newcommand{\Lan}{\mathcal{L}}
\newcommand{\Ln}{\lim\limits_{n\to \infty}}
\newcommand{\clist}{\mathfrak{c}_{1}, \cdots, \mathfrak{c}_m}
\newcommand{\morph}[1]{\stackrel{#1}{\simeq}}
\newcommand{\vlst}[2]{#1_1,\dots, #1_{#2}}
\newcommand{\gnp}{G(n,\beta_1/n^{a_1-1}, \dots,\beta_l/n^{a_l-1})}

\begin{document}
\begin{abstract}
	The goal is to generalize the results from Lynch (1992) on the convergence law for sparse random graphs to sparse random hypergraphs. This requires in particular an understanding of Lynch's techniques, based on Ehrenfeucht-Fraïssé games, an analysis of the structure of sparse random hypergraphs.
\end{abstract}
\tableofcontents

@@

@@

After this is archived the theorem follows easily. Indeed, let $\phi$ be a sentence 
in the first order language $\Lan$ of graphs whose quantifier rank is $k$, and denote by
$G$ a random graph in $G(n,\beta/n)$. \par

@@

\section{Agreeability Classes}

@@

\chapter{First Order Logic of Sparse Random Hypergraphs}

\section{Basic definitions and conventions.}

\subsection{General relational structures.}

Given a natural number $n$, we will use the notation
$[n]:= \{1,\dots, n\}$. We will denote by $S_n$
the symmetric group on $[n]$, and by $\Delta_n$ the 
diagonal set $\{(a,a)\in [n]^2 \}$. \par
Given a set $X$, then $S_n$ acts on $X^n$ in an evident way. That is, 
given $g\in S_n$ and $(x_1, \dots, x_n)$ one can define
\[ g \cdot (x_1,\dots,x_n) =(y_1,\dots,y_n), \]
where $y_{g(i)}=x_i$ for all $1\leq i\leq n$.\par
Given $\Phi$ a subgroup of $S_n$ we will denote by $X^n/\Phi$
the orbit set associated to the action of $\Phi$ over $X^n$.\par
We will use the notation $[x_1,\dots,x_n]$ to refer to the 
equivalence class of the $n$-tuple $(x_1,\dots, x_n)$ in 
any sort of quotient $X^n/\Phi$. That is, while the notation
$(x_1,\dots, x_n)$ will be reserved to ordered $n$-tuples, 
$[x_1,\dots,x_n]$ will denote an ordered $n$-tuple modulo the
action of some arbitrary group of permutations. Which group is this 
will depend solely on the ambient set where $[x_1,\dots,x_n]$ is
considered.
\par

\begin{definition}
	Let $n,a\in \N$, let $\Phi$ be a subgroup of $S_a$, and let
	$A$ be a subset 
	\[ A\subseteq [a]^2 \setminus \delta.\]
	The total edge set $\mathcal{H}_{(a,\Phi, A)}(n)$ of size $a$, 
	symmetry group $\Phi$ and
	restrictions $R$ on $n$ elements is the set:
	\[  \mathcal{H}_{(a,\Phi, R)}(n)= ([n]^a/\Phi) \, \,
	\setminus \{\,  [x_1, \dots,x_a] \in [n]^a/\Phi  \, \, 
	| \, \, x_i=x_j \, \text{for some } (i,j)\in R \} \]
\end{definition}

\begin{definition}
	An (hyper)-graph $([n], H_1,\dots, H_c)$ with edge colors 
	$1,\dots, c$, sizes $a_1,\dots,a_c$, 
	symmetry groups $\Phi_1,\dots,\Phi_c$ and 
	restrictions $A_1,\dots,A_c$ consists of 
	\begin{itemize}
		\item The set $[n]$ for some natural number $n$.
		\item For $i=1,\dots,c$, a colored edge set $H_i\subseteq \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ whose elements 
		have color $i$.
	\end{itemize}
\end{definition}

\begin{definition} 
	Let $p=(p_1,\dots, p_c)$, where all $p_i$'s are real numbers
	between $0$ and $1$. 
	The random model $HG(n,p)$ with edge colors $1,\dots,c$,
	sizes $a_1,\dots,a_c$, 
	symmetry groups $\Phi_1,dots,\Phi_c$ 
	and restrictions $A_1,\dots,A_c$, is the one that
	assigns to each graph $G=([n], H_1,\dots, H_c)$
	probability
	\[ Pr(G)=\prod_{i=1}^{c} p_i^{|H_i|}(1-p_i)^{|\mathcal{H}_{(a_i,\Phi_i,A_i)}(n)|-|H_i|}.	
	\]
	Equivalently, this is the probability space obtained by 
	assigning to each colored edge 
	$e\in \mathcal{H}_{(a_i,\Phi_i,A_i)}(n)$ probability $p_i$ independently. 
\end{definition}

For the rest of the work we will consider 
\begin{itemize}
	\item the total number of colors $c$,	
	\item the sizes $a_1,\dots,a_c$,
	\item the symmetry group $\Phi_1,\dots, \Phi_c$ and,
	\item the restrictions $A_1,\dots,A_l$
\end{itemize}
fixed. When we say ``graph'' from now on what
we will mean is ``hiper-graph with edge colors 
$1,\dots, c$, sizes $a_1,\dots,a_c$, 
symmetry groups $\Phi_1,\dots,\Phi_c$ and 
restrictions $R_1,\dots,R_c$''. \par

Given a graph $G=([n], H_1,\dots, H_c)$ we will denote by
$H_i(G)$ the edge set $H_i$, and by $V[G]$ the vertex set
$[n]$. Also, we will write $H(G)$ to denote the 
disjoint union of colored sets $\cup_{i=1}^c H_i$.
This way, an edge $e\in H(G)$ with color $i$ is an element
$[x_1,\dots,x_{a_i}]\in H_i(G)$, and the $x_i$'s are vertices
belonging to $V(G)$. \par
Given a set of vertices, $X\subseteq V(G)$, we will denote
the by $G[X]$ the induced sub-graph on $X$. \par
As usual, we will sometimes treat edges as sets of vertices
rather than ``tuples modulo the action of some permutation group''. 
This way, expressions like $e_1\cup e_2$ for $e_1, e_2\in H(G)$
will make sense and mean 
``the set of vertices that occupy some place in $e_1$ 
and in $e_2$".\par
Some other times we will treat edges $e\in H(G)$
as sub-graphs of $G$ in the evident way. That is, the subgraph
denoted by $e$ is the one whose vertex set is $e$-i.e., the vertices in $e$-
and whose only edge is $e$. 
This way, when we have some edges $e_1,\dots, e_l\in H(G)$ 
it will make sense to talk
about the subgraph $\cup_{i=1}^l e_i$, which is the graph
whose vertex set is the set of vertices belonging to the $e_i$'s, 
and whose edges are exactly the $e_i$'s. In spite of these
abuses of notation the ``type'' of any ``term'' involving edges 
should be derivable from the context. \par
Another usual abuse of notation we will make is to sometimes
treat graphs as their underlying vertex sets. Hence,
expressions defined for sets of vertices will also be defined 
for graphs.

\subsection{The First Order Language}

From now on when we talk about ``first order formulas" 
will be referring to formulas in the first order relational 
language $\mathcal{L}$ with relations $R_1,..., R_c$ of arities
$a_1,\dots, a_c$ respectively. \par

Graphs are $\mathcal{L}$-structures in an evident way. 
The universe of a graph $G$ is $V(G)$, and for each 
$1\leq i \leq c$ and any $x_1,\dots, x_{a_i}$ we say 
\[R_i(x_1,\dots,x_{a_i}) \text{ if } [x_1,\dots, x_{a_i}]\in H_i(G).\] 
That is, variables in $L$ are interpreted as vertices in $G$ and
relations are interpreted as edges. By definition, all graphs $G$ 
satisfy the formulas
\begin{itemize}
	\item Symmetry formulas:
	\[ S_g: =\big( R_i(x_1\dots,x_{a_i})\iff R_i(x_{j_1}\dots,x_{j_{a_i}})\big) ,\]
	where the the index $j_k$ is $g(k)$, and $g$ is an element from $\Phi_i$.
	\item Anti-reflexivity formulas:
	\[A_{i,(j,l)}:=\big(R_i(x_1\dots,x_{a_i})\implies 
	\neg(x_j= x_l)\big),\]
	where $(j,l)\in A_i$.
\end{itemize}

\section{The Theorem.}

From now on we will adopt the following two conventions:
\begin{itemize}
	\item We will always work in the random model $HG(n,p(n))$, where
	$p(n)=p(n,\beta)$ is defined as the tuple
	$(\beta_1 n^{1-a_1},\dots, \beta_c n^{1-a_c})$, and
	$\beta=(\beta_1,\dots, \beta_c)$.
	The symbols $\beta_1,\dots, \beta_c$
	denote positive real variables,
	but for the most part we will 
	treat them as arbitrary positive real constants.
	\item The first order language we will always refer to is the one 
	defined in last section, $\mathcal{L}$. 
\end{itemize}

We define $\Lambda$ and $M$ as the minimal families
of expressions with arguments $\beta_1,\dots, \beta_c$ that satisfy the conditions:
\begin{itemize}
	\item $1\in \Lambda$
	\item For any $\mu\in M$ and any $n\in \N$ both
	$Poi_{\mu}(n)$ and $Poi_\mu(\geq n)$ are in $\Lambda$
	\item For any $\lambda_1,\lambda_2 \in \Lambda$, the
	product $\lambda_1\lambda_2$ belongs to $\Lambda$ as well.
	\item For any $l,a,i\in \N$ with $1\leq i \leq c$,
	$a > 0$, and $\lambda_1,\dots, \lambda_l\in \Lambda$,
	the expression $\frac{\beta_i \prod_{j=1}^{l}\lambda_j}{a}$
	belongs to $M$.		
\end{itemize}
We also define another families $\widehat{\Theta}$ and $\Theta$ of expressions with arguments
$\beta_1,\dots, \beta_c$ as the minimal one satisfying:
\begin{itemize}
	\item For any $l,s,a\in \N$ with $a>0$ and any 
	non-necessarily-different $\lambda_1,\dots, \lambda_l\in \Lambda$,
	$\alpha_1,\dots,\alpha_s\in \{\beta_1,\dots \beta_c\}$,
	the expression 
	\[\frac{\left(\prod_{i=1}^{l} \lambda_i \right)
		\left( \prod_{i=1}^{s}\alpha_i \right)}{a}\] 
	lies in $\widehat{\Theta}$.
	\item For any $g\in \widehat{\Theta}$ and any $n\in \N$ both
	$Poi_g(n)$ and $Poi_g(\geq n)$ are in $\Theta$.
	\item For any $\theta_1, \theta_2\in \Theta$ the product
	$\theta_1\theta_2$ belongs to $\Theta$ as well.
\end{itemize}

For any first order sentence $\phi$
we will use the notation 
$Pr_n(\phi):=Pr(HG(n,p(n))\models \phi)$. \par

The rest of the work will be devoted to prove the following theorem:

\begin{theorem}\label{thm:THEONE} 
	Let $\beta=(\beta_1,\dots, \beta_c)$, and let $\psi$ be a 
	F.O sentence in $\mathcal{L}$. Then the function
	\[
	\mathfrak{F}(\beta):=\Ln Pr(\, HG(n,p(\beta,n))\, \models \, \psi \,)
	\]
	is well defined for all values of $\beta$ and it is a finite sum 
	of expressions in $\Theta$.
\end{theorem}

\section{Sub-critical, Critical and Super-critical Graphs.}

We define a distance over arbitrary graphs $G$. For each $x, y\in V(G)$,
\[ d(x,y)= \min_{\substack{H \text{ subgraph of } G\\ 
H \text{ connected }\\
x,y\in V(H)}} |V(H)| - 1 .\]
That is, the distance between $x$ and $y$ is the minimum size
of a connected graph $H$ containing both. 
If such graph does not exist we define $d(x,y)=\infty$.
This definition extends naturally to subsets $X,Y\subseteq V(G)$:
\[ d(X,Y)=\min_{\substack{x\in X\\ y\in Y}} d(x,y).\]
As usual, when $X=\{x\}$ we will omit the brackets and write
$d(x,Y)$ instead of $d(\{x\},Y)$, for example.  \par

@@

\begin{proposition}\label{prop:pathform}
	A path $P$ between $x$ and $y$ in a graph $G$ is a union of 
	edges $e_1,\dots, e_l\in H(G)$ such that
	\begin{itemize}
		\item $x$ only belongs to
		$e_1$ and $y$ only belongs to $e_l$.
		\item For any $1\leq j < i\leq l$, $e_i$ intersects
		$e_j$ if and only if $i=j+1$.
	\end{itemize}  	
\end{proposition}
\begin{proof}[Sketch of the proof.]
	Proceed by induction on the number of edges.
\end{proof}

\begin{definition}
	The likelihood $L(G)$ of an hypergraph $G=(V,E_1,\dots,E_l)$ is
	the number
	\[ \left( |V(G)| - \sum_{i=1}^l |H_i(G)\langle Ta_i-1)\right).\]
	An hypergraph is $L$-balanced if it contains no subgraph with
	less likelihood than itself. 
\end{definition}

Given a graph $G$, and an edge $e\in H(G)$ of color $i$,
the operation of ``cutting'' the edge $e$ is the one where we remove 
$e$ from $H_i$ and afterwards we also remove the isolated 
vertices from the resulting graph.

\begin{proposition} \label{prop:balanced}
	Any connected graph $G$ is $L$-balanced. 
\end{proposition}
\begin{proof}
	\begin{proof}[Sketch of the proof.]
		Suppose $G$ is non-empty.
		The proof is by induction on the number of edges in $G$. 
		\item If $G$ has zero edges it is an isolated vertex so the statement is true.
		\item Suppose that $G$ has $m>0$ edges. Choose a vertex $x\in V(G)$ and
		an edge $e\in H(G)$ such that the distance from the $x$ to $e$ is maximum. 
		The subgraph $F$ obtained from cutting $e$ must be connected, so by the
		induction hypothesis $F$ is balanced. 
		The original graph $G$ was connected, 
		so $e$ must intersect $F$ in at least one vertex, and
		\begin{equation}\label{eqn:balanced}
		L(G)\leq L(F).
		\end{equation}
		Suppose that $G$ contains a sub-graph $G_2$ with 
		$L(G_2)<L(G)$. Then, as $F$ is $L$-balanced and
		\ref{eqn:balanced} holds, $e\in H(G_2)$. Call $F_2$
		to the result of cutting $e$ in $G_2$. Then
		$F_2$ is a subgraph of $F$ and one can check
		\[ L(F_2) - L_(G_2) \leq L(F)-L(G).\]
		In consequence, as $L(F)-L(F_2)$ is non-positive, 
		so is $L(G)-L(G_2)$, arriving at a contradiction.
	\end{proof}
\end{proof}

\begin{corollary}
	A (non-empty) connected graph $G$ cannot have more likelihood than $1$.
\end{corollary}
\begin{proof}
	A because of the previous proposition $G$ is $L$-balanced.
	If $G$ is non-empty it contains some vertex,
	and vertices have likelihood $1$.
\end{proof}

\begin{definition} 
	We will call sub-critical, critical and super-critical
	graphs to $L$-balanced graphs with likelihood greater than
	zero, zero, and less than zero respectively. 
\end{definition}

\begin{definition}
	A cluster is a connected graph $G$ with non-positive likelihood such 
	that all of its subgraphs $T$ have greater likelihood
	than itself. 
\end{definition}

We will call unicycles to connected critical graphs, and cycles
to minimal unicycles. In particular, cycles are clusters.

\begin{proposition}
	Any unicycle contains exactly one cycle. 
\end{proposition}
\begin{proof}[Sketch of the proof.]
 	Suppose the unicycle $G$ contains two different cycles $F_1,F_2$.
 	\item If $F_1$ and $F_2$ have nonempty intersection then $F_1\cup F_2$ 
 	has negative likelihood.
 	\item Otherwise, consider a path $P$ between two vertices $x\in V(F_1)$
 	and $y\in V(F_2)$. The union $F_1\cup F_2 \cup P$ has negative likelihood.
\end{proof}

\begin{proposition}
	A cycle $G$ is either:
	\begin{itemize}
		\item[(1)] An edge $e$ where exactly one vertex appears exactly
		twice.
		\item[(2)] A path $P$, with $L(P)=1$
		between two vertices $x$ and $y$, with
		$L(P)=1$, together with an edge $e$ that intersects $P$ exactly
		in $x$ and $y$.
	\end{itemize}
\end{proposition} 
\begin{proof}[Sketch of the proof.]
	\item If $G$ contains only one edge then (1) holds necessarily.

	\item Otherwise, $G$ cannot contain an edge that intersects the rest of the graph
	only in one vertex, because cutting it would yield a smaller connected 
	graph with likelihood $0$.

	This way, by double counting one can obtain that 
	each edge intersects the rest of $G$ exactly in two vertices.
	Choose an edge $e\in H(G)$ and call $F$ to the graph obtained by
	cutting $e$ in $G$. The intersection $e\cup F$ contains exactly two 
	vertices, $x, y$. The graph $F$ must be 
	\begin{itemize}
		\item Connected. Otherwise one of its connected components would have
		likelihood $0$ or less.
		\item A path between $x$ and $y$. Otherwise it contains a path $P$ between
		$x$ and $y$ and $P\cup E$ has likelihood $0$. 
	\end{itemize} 
	Thus (2) holds, as we wanted. 
\end{proof}

Given a graph $G$, its diameter $diam(G)$ will be the maximum distance
between any two of its vertices:
\[diam(G)=\max_{\substack{x,y\in V(G)}} d(x,y).\]

\begin{corollary}\label{cor:finitecycles}
	For any $r\in \N$ there is a finite number of 
	cycles with diameter at most $r$.
\end{corollary}
\begin{proof}[Sketch of the proof]
	Let $G$ be a cycle with $diam(G)=r$, and let
	$x,y\in V(G)$ be such that $d(x,y)=r$. Let $e$
	be an edge containing $y$ and not $x$. If such edge
	does not exists then $G$ is composed of at most two edges.
	Otherwise
	consider $F$ the graph resulting from cutting $e$ in $G$. 
	One can check that $F$ must be a path of size at most $2r$, 
	and there are a finite number of those.
	In consequence we can represent all cycles of diameter $r$
	either as an edge, as an union of two edges, or as an
	union of a path with size at most $r$ with an edge. 
	In particular $|V(G)|\leq 2r+2a$, where $a$ is the
	maximum of $a_1,\dots, a_c$.
\end{proof}

\begin{proposition}
	A cluster is a connected graph $G$ where each edge
	$e\in H(G)$
	satisfies at least one of the following:
	\begin{itemize}
		\item[(1)] $e$ intersects the union of all the other edges
		in $H(G)$ in at least two vertices.
		 \item[(2)] $e$ contains some vertex at least twice.
	\end{itemize}
\end{proposition}
\begin{proof}
	Suppose that $e\in H(G)$ satisfies neither (1) nor (2). Then
	the graph $G^\prime$ obtained from cutting $e$ in $G$ is a subgraph
	of $G$ with
	\[L(G^\prime)= L(G).\]
	In consequence $G$ is not a cluster. 
\end{proof}

\begin{definition} 
	A tree is a connected graph with likelihood $1$.
\end{definition}

\begin{proposition} There is a unique path between any two vertices of a tree. 
\end{proposition}
\begin{proof}[Sketch of the proof]
	Let $T$ be a tree. Suppose there are 
	two vertices $x, y\in V(T)$
	with two different paths, $P_1,P_2$, between them. 
	Then the graph $P_1\cup P_2$ would have non positive
	likelihood, contradicting \cref{prop:balanced}.
\end{proof}

\begin{proposition}
	A tree $T$ is a graph obtained from successively adding edges to a single
	vertex in such a way that any new edge intersects the current graph
	in exactly one vertex. 
\end{proposition}
\begin{proof}[Sketch of the proof.]
	Choose a vertex $x\in V(T)$ and an edge $e\in H(T)$ such that 
	the distance between the two is the maximum one. Call $T_2$
	to the graph obtained by cutting $e$ in $T$. The graph $T_2$ 
	is a tree and intersects $e$ in exactly one vertex. 
	One can continue this process until reaching a single edge.
	Repeating the process backwards now, adding the removed 
	edges successively, yields the result.  	
\end{proof}

\section{Agreeability classes. Winning Strategy For Duplicator}

We define the set of constants symbols as
$Const:=\{\mathfrak{c}_i\}_{i\in \N, \, i>0}$.
For any $n\in \N$, $n>0$, let $Const_n$ be the set $\{\mathfrak{c}_1,\dots,\mathfrak{c}_n\}$. 
A co-labeling of a graph $G$ is a map $\nu:Const_n\rightarrow V(G)$,
where for some $n>0$. Given $\mathfrak{c}_i\in Const_n$, 
we will say that the vertex $\nu(\cc_i)$ is labeled $\cc_i$.
Equivalently, we can denote a labeling $\nu$ as a tuple
$(\cc_{1}[x_1],\dots, \cc_m[x_m])$ where each 
$x_j$ in $V(G)$ labeled $\cc_j$.

\begin{definition} 
	A graph with constants $G(\clist)$ is graph $G$
	together with a co-labeling $(\cc_{1}[x_1],\dots, \cc_m[x_m])$. 
\end{definition}

To keep our notation compact we will often drop 
he $x_i$'s and say $G(\cc_1,\dots, \cc_m)$ and 
sometimes we will even omit the $(\cc_1,\dots, \cc_m)$ and
denote by $G$ the graph with constants when the co-labeling is not 
relevant. \par
We will often identify constants $\cc_i$ with their labeled vertices
$\nu(\cc_i)$. This should not lead to confusion. 
However, note that for two
different indices $i,j$, $\nu(\cc_i)$ and $\nu(\cc_j)$
may be the same vertex,
but the constant symbols $\cc_i$ and $\cc_j$ are different.\par

@@

Given $x\in V(G)$ and $X\subseteq V(G)$ we define the
neighbourhood graphs $N(x;r)$ and $N(X;r)$ as
\[ N(x;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(x,y)\leq r \, \} \]
\[ N(X;r)= G[S], \quad \text{where } S=\{\, y\in V(G) \, | d(X,y)\leq r \, \}, \]
for each $r\in \N$.

\begin{definition}
	 A rooted tree $(T,x)$ is a tree $T$ with a distinguished vertex 
	 $x$ called root.
	 The radius of the tree is the 
	 maximum distance between its root and any
	 of its vertices.  
	 The initial edges of $(T,x)$ are the edges in $T$ containing
	 the root.
\end{definition}

We will often omit the root and denote by $T$ the whole rooted tree $(T,x)$.\par

In a rooted tree $(T,x)$ all the edges can be rooted in a canonical way. 
The root of an edge $e$ is the vertex $y\in e$ such that $d(x,y)=d(x,e)$.

\begin{definition}
	Let $G(\clist)$ be a graph with constants and $X,Y\subset V(G)$. Then
	$Tree(x,G)$ is the rooted tree $(G[V_x],x)$, where
	\[ V_x= \{\, y\in V \, | \, d(Center(G),y)= d(Center(G),x)+ d(x,y) \,	 \}. \]
\end{definition}

Informally, $Tree(x,G)$ is the graph composed of all the vertices that
have to pass through $x$ in order to reach $Center(G)$.

\begin{remark}
	The graph $Tree(x,G)$ is indeed a tree.
\end{remark}

When $(T,x)$ is a rooted tree, we will use the notation
\[ Tree(y, T):= Tree(y,T(\cc_1[x])). \]
That is, $Tree(y,T)$ is the tree that ``hangs from $y$'' in
$T$.

When the ``environment graph'' is clear we will write $Tree(x)$
instead of $Tree(x,G)$.

\begin{definition} 
	The $k$-morphism equivalence relation $\morph{k}$ between rooted trees
	of the same radius,
	and the $k$-type of an edge in a rooted tree,
	are defined inductively as follows:

	\begin{itemize}
		\item If $T_1$ and $T_2$ are radius $0$ rooted trees then they consist only of their roots and $T_1\morph{k} T_2$. 
		\item The radius of a $k$-morphism class of rooted trees $C$
		is the radius that all trees in $C$ have.
		\item Let $T$ be a rooted tree of radius $r$. The $k$-type
		of an edge 
		\[e=[x_1,\dots, x_{j-1}, x ,x_j, \dots, x_{a_d-1}]\in H(T)\]
		with color $d$, where $x$ is the root of $e$, is the colored 
		``tuple modulo the action of $\Phi_d$'' 
		\[E=[C_1,\dots, C_{j-1}, \mathfrak{r}, C_j,\dots, C_{a_d -1}]
		,\]
		with dolor $d$, where
		\begin{itemize}
			\item $\mathfrak{r}$ is the ``root symbol''
			\item $C_i$ is the $k$-morphism class of the tree
			$Tree(x_i,T)$, for $1\leq i \leq a_d-1$.
		\end{itemize} 
		The radius of $E$ is the maximum radius of any of the
		$C_i$'s.

		\item If $T_1$ and $T_2$ are trees of radius $r>0$ and roots $x$ and $y$, then $T_1\morph{k} T_2$ means that for any $k$-type of edges $E$
		with radius less than $r$ at least one of the following is satisfied:
		\begin{itemize}
			\item The number of initial edges in $T_1$ and $T_2$ of $k$-type $E$ 
			is the same.
			\item both $T_1$ and $T_2$ contain no less than $k+1$
			initial edges of $k$-type $E$. 
		\end{itemize}
	\end{itemize}
\end{definition}

\begin{remark}
	If $(T,x)$ is a rooted tree with radius 
	$r$, any initial edge $e\in H(T)$ has ($k$-type
	of) radius less than $r$.
\end{remark}
